An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/learner.tex
add algorithm

\begin{algorithm}
\STATE Let $\theta$ be the list of possible types for the intermediate representation of interest.
\caption{Probabilistically Learn Rules}
  \begin{algorithmic}[1]
    \STATE learnRules($C$):\\
    Input: $C$ contains intermediate representations\\ 
     \qquad \enspace \enspace of configuration files\\
%    Intermediate Representation of configuration file, $M$, where the $i$-th entry of $M$ is denoted by $M_i$\\
    \FOR{each file $F$ in $C$}
        \FOR{each entry $e$ in $F$}
               \IF{$g(e)$ is false}
                        \STATE continue to next entry
               \ENDIF
                \FOR{$\tau \in typelist(e)$}
                        \FOR{$t \in templates(\tau)$}
                        \IF{$t$ is satisfied over appropriate tuples of arity$(\tau)$ entries, where one of the arguments is $v(e)$ and rest of the tuple is taken from the remaining entries with types matching $t$ in their type lists}
                                        \STATE update $p_{\tau}$ appropriately
%                                \ELSIF{anti($t$) is satisfied over rest of entries}
%                                        \STATE update $p_{\tau}$ appropriately
                                \ENDIF
                        %Check if $t$ is satisfied  over rest 
                        \ENDFOR
               \ENDFOR
          \ENDFOR
      \ENDFOR
  \end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm}
%\State Let $\theta$ be the list of possible types for the intermediate representation of interest.
\caption{Probabilistically Learn Rules}
  \begin{algorithmic}[1]
    \State learnRules($C$):\\
    Input: $C$ contains intermediate representations\\ 
     \qquad \enspace \enspace of configuration files\\
    Intermediate Representation of configuration file, $M$, where the $i$-th entry of $M$ is denoted by $M_i$\\
    \For{each file $F$ in $C$}
        \For{each entry $e$ in $F$}
               \If{$g(e)$ is false}
                        \State continue to next entry
               \EndIf
                \For{$\tau \in typelist(e)$}
                        \For{$t \in templates(\tau)$}
                        \If{$t$ is satisfied over appropriate tuples of arity$(\tau)$ entries, where one of the arguments is $v(e)$ and rest of the tuple is taken from the remaining entries with types matching $t$ in their type lists}
                                        \State update $p_{\tau}$ appropriately
                                \ElsIf{anti($t$) is satisfied over rest of entries}
                                        \State update $p_{\tau}$ appropriately
                                \EndIf
                        %Check if $t$ is satisfied  over rest 
                        \EndFor
               \EndFor
          \EndFor
      \EndFor
  \end{algorithmic}
\end{algorithm}
